Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-21 outputs/paper/paper.qmd
limitations section edits

#| label: tbl-hatemodel
#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."
#| 
table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
  set_escape_contents(FALSE) |>
  add_rows(c("sociodemographics ", " ", " ", "X", "X", "X", "X"), after = 7)  |>
  add_rows(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
  add_rows(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
  add_rows(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)

@@

>>>>

#| label: tbl-hatemodel
#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."

table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
  set_escape_contents(FALSE) |>
  add_rows(c("sociodemographics ", " ", " ", "X", "X", "X", "X"), after = 7)  |>
  add_rows(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
  add_rows(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
  add_rows(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)

@@

Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper]. Despite the survey being long, it can not be considered to be comprehensive. This prevented us from exploring other relationships in the data. For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War II. Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.

 Due to the heteronormative nature of this study’s data, our analysis was also not able to be fully representative of the German population as [@main_paper]’s authors described. While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.

There were also limitations associated with missing and limited data in our set. For example, in our analysis depicted in @fig-excess, fewer than 300 observations were represented in the oldest age group, which these authors doubted was enough for a meaningful evaluation.
